---
title: "R Notebook"
output: html_notebook
---

1. clean the data

```{r}
# Load required packages
library(dplyr)
library(nonlinearTseries)
library(tseriesChaos)
library(plot3D)
library(scatterplot3d)
library(rgl)
library(ggplot2)
library(Hmisc)
options(scipen = 999)  # Turn off scientific notation

# Define file path
file_path <- "/Users/nuoxu/Desktop/complex system group work/D1_sensor_data.csv"

# Check if file exists
if (!file.exists(file_path)) {
  stop("File does not exist, please check the path: ", file_path)
}

# Load data
bee_df <- read.csv(file_path, stringsAsFactors = FALSE)

# Preview the first few rows
cat("First few rows of the data:\n")
print(head(bee_df))

# Convert columns to appropriate types
bee_df$temperature <- as.numeric(bee_df$temperature)
bee_df$humidity <- as.numeric(bee_df$humidity)
bee_df$hive_power <- as.numeric(bee_df$hive_power)
bee_df$tag_number <- as.numeric(bee_df$tag_number)
bee_df$published_at <- as.POSIXct(bee_df$published_at, format = "%Y-%m-%d %H:%M:%S+00:00", tz = "UTC")

# Check for NAs introduced during conversion
cat("Data summary after conversion:\n")
print(summary(bee_df[, c("temperature", "humidity", "hive_power", "tag_number", "published_at")]))

# Filter for hive 202204
hive_data <- bee_df %>%
  dplyr::filter(tag_number == 202204) %>%
  dplyr::select(published_at, temperature, humidity, hive_power)

cat("Initial number of records for hive 202204: ", nrow(hive_data), "\n")

# Remove duplicates based on published_at
hive_data <- hive_data %>%
  dplyr::distinct(published_at, .keep_all = TRUE)

cat("Number of records after removing duplicates: ", nrow(hive_data), "\n")
cat("Time range of the data:\n")
print(range(hive_data$published_at, na.rm = TRUE))

# Remove missing values
hive_data <- na.omit(hive_data)

# Sort by timestamp
hive_data <- hive_data %>% dplyr::arrange(published_at)

# Subsampling: Reduce from ~8000 to ~1000 points by taking every 8th point
subsample_idx <- seq(1, nrow(hive_data), by = 8)
hive_data <- hive_data[subsample_idx, ]

# Extract variables
temperature <- hive_data$temperature
humidity <- hive_data$humidity
hive_power <- hive_data$hive_power

cat("Data length after subsampling: ", length(temperature), "\n")
cat("Subsampling reduces computational load but may lose high-frequency dynamics.\n")
cat("We sample every 8th point (~12.5% of data) to retain main dynamic features.\n")
```

2. plots
```{r}
# Exploratory Visualizations (Before Phase Space Reconstruction)

# 1. Time Series Plot for temperature, humidity, and hive_power
plot(temperature, type = "l", col = "blue", xlab = "Time", ylab = "Value", 
     main = "Time Series of Temperature, Humidity, and Hive Power")
lines(humidity, col = "green")
lines(hive_power, col = "red")
legend("topright", legend = c("Temperature (째C)", "Humidity (%)", "Hive Power"), 
       col = c("blue", "green", "red"), lty = 1)

# 2. Pairwise X-Y Plots to explore relationships between variables
# Temperature vs Humidity
plot(temperature, humidity, type = "p", col = "purple", 
     xlab = "Temperature (째C)", ylab = "Humidity (%)", 
     main = "Temperature vs Humidity")

# Temperature vs Hive Power
plot(temperature, hive_power, type = "p", col = "orange", 
     xlab = "Temperature (째C)", ylab = "Hive Power", 
     main = "Temperature vs Hive Power")

# Humidity vs Hive Power
plot(humidity, hive_power, type = "p", col = "brown", 
     xlab = "Humidity (%)", ylab = "Hive Power", 
     main = "Humidity vs Hive Power")

# 3. Change Time Series (Velocity) Plots
# Calculate change (first-order difference) for each variable
hive_data$temp_lag1 <- Lag(hive_data$temperature, 1)
hive_data$temp_lead1 <- Lag(hive_data$temperature, -1)
hive_data$temp_change <- (hive_data$temp_lead1 - hive_data$temp_lag1) / 2

hive_data$humidity_lag1 <- Lag(hive_data$humidity, 1)
hive_data$humidity_lead1 <- Lag(hive_data$humidity, -1)
hive_data$humidity_change <- (hive_data$humidity_lead1 - hive_data$humidity_lag1) / 2

hive_data$hive_power_lag1 <- Lag(hive_data$hive_power, 1)
hive_data$hive_power_lead1 <- Lag(hive_data$hive_power, -1)
hive_data$hive_power_change <- (hive_data$hive_power_lead1 - hive_data$hive_power_lag1) / 2

# Plot change time series
plot(hive_data$temp_change, type = "l", col = "blue", 
     xlab = "Time", ylab = "Change in Value", 
     main = "Change Time Series of Temperature, Humidity, and Hive Power")
lines(hive_data$humidity_change, col = "green")
lines(hive_data$hive_power_change, col = "red")
legend("topright", legend = c("Temperature Change", "Humidity Change", "Hive Power Change"), 
       col = c("blue", "green", "red"), lty = 1)

# 4. Vector Field with Density Plot (Temperature vs Humidity vs humidity)
# Ensure change variables are calculated (if not already done)
hive_data$temp_lag1 <- Lag(hive_data$temperature, 1)
hive_data$temp_lead1 <- Lag(hive_data$temperature, -1)
hive_data$temp_change <- (hive_data$temp_lead1 - hive_data$temp_lag1) / 2

hive_data$humidity_lag1 <- Lag(hive_data$humidity, 1)
hive_data$humidity_lead1 <- Lag(hive_data$humidity, -1)
hive_data$humidity_change <- (hive_data$humidity_lead1 - hive_data$humidity_lag1) / 2

hive_data$hive_power_lag1 <- Lag(hive_data$hive_power, 1)
hive_data$hive_power_lead1 <- Lag(hive_data$hive_power, -1)
hive_data$hive_power_change <- (hive_data$hive_power_lead1 - hive_data$hive_power_lag1) / 2

# Remove NAs introduced by lagging
hive_data <- na.omit(hive_data)

# Calculate change magnitude as a proxy for density
change_magnitude <- sqrt(hive_data$temp_change^2 + hive_data$humidity_change^2 + hive_data$hive_power_change^2)

# Normalize change magnitude to map to a color gradient
density_colors <- (change_magnitude - min(change_magnitude)) / (max(change_magnitude) - min(change_magnitude))
# Map to a color gradient (e.g., from blue to red)
colors <- colorRampPalette(c("blue", "red"))(100)
point_colors <- colors[as.integer(density_colors * 99) + 1]

# 3D Plot with vector field and density (using color to represent density)
plot3d(hive_data$temperature, hive_data$humidity, hive_data$hive_power, 
       col = point_colors, size = 1,  # Fixed size for all points
       xlab = "Temperature (째C)", ylab = "Humidity (%)", zlab = "Hive Power", 
       main = "Vector Field and Density Plot (Temp vs Humidity vs Hive Power)")

# Add line segments to represent the vector field using segments3d
for (i in 1:nrow(hive_data)) {
  segments3d(x = c(hive_data$temperature[i], hive_data$temperature[i] + hive_data$temp_change[i]),
             y = c(hive_data$humidity[i], hive_data$humidity[i] + hive_data$humidity_change[i]),
             z = c(hive_data$hive_power[i], hive_data$hive_power[i] + hive_data$hive_power_change[i]),
             col = "black", lwd = 1)
}
```


```{r}
# Modified function to diagnose and fix the NA issue for humidity
perform_phase_space_reconstruction_humidity <- function(data, var_name) {
  # Step 1: Check data characteristics
  cat("Summary of ", var_name, " data:\n")
  print(summary(data))
  cat("Standard deviation of ", var_name, ":", sd(data), "\n")
  cat("Variance of ", var_name, ":", var(data), "\n")
  if (any(is.na(data))) stop("Data contains NA values, please clean the data.")
  if (sd(data) == 0) stop("Data has zero variance, cannot perform phase space reconstruction.")

  # Plot the time series to inspect its behavior
  plot(data, type = "l", col = "green", xlab = "Time", ylab = "Humidity (%)", 
       main = "Time Series of Humidity")

  # Plot histogram to inspect distribution
  hist(data, breaks = 30, col = "lightgreen", xlab = "Humidity (%)", 
       main = "Histogram of Humidity")

  # Calculate standard deviation for parameter setting
  sd_data <- sd(data)
  if (is.na(sd_data) || sd_data == 0) sd_data <- (max(data) - min(data)) / 4

  # Step 2: Determine time delay (tau) using ACF and AMI
  tau_acf <- find_acf_local_min(data, lag.max = 100)
  plot(acf(data, lag.max = 100, plot = FALSE), type = "h", main = paste("ACF Plot for", var_name))
  abline(h = 0.2, col = "red", lty = 2)

  tau_ami <- timeLag(data, technique = "ami", lag.max = 100, do.plot = TRUE)
  if (inherits(tau_ami, "try-error")) tau_ami <- tau_acf + 2

  cat("For ", var_name, ":\n")
  cat("ACF-based tau:", tau_acf, "\nAMI-based tau:", tau_ami, "\n")
  cat("We choose AMI-based tau (", tau_ami, ") as it is more suitable for nonlinear systems (Wiltshire, 2025).\n")
  tau <- tau_ami

  # Step 3: Try different tau values to estimate M
  tau_candidates <- c(tau_ami, tau_acf, 5)  # Test AMI tau, ACF tau, and a smaller tau (5)
  emb_dim <- NA
  for (t in tau_candidates) {
    cat("Trying tau =", t, "to estimate M...\n")
    emb_dim_temp <- estimateEmbeddingDim(data, time.lag = t, max.embedding.dim = 15, do.plot = TRUE)
    if (!is.na(emb_dim_temp)) {
      emb_dim <- emb_dim_temp
      tau <- t
      cat("Found valid M =", emb_dim, "with tau =", t, "\n")
      break
    }
  }

  # If still NA, set a default M
  if (is.na(emb_dim)) {
    cat("Warning: estimateEmbeddingDim returned NA for ", var_name, " with all tested tau values.\n")
    cat("Possible reasons: data may be too smooth, random, or noisy.\n")
    cat("Setting default M = 3.\n")
    emb_dim <- 3
  }
  M <- max(emb_dim, 3)
  cat("Final tau for ", var_name, ":", tau, "\n")
  cat("Estimated M for ", var_name, ":", emb_dim, "\n")
  cat("We choose M =", M, "for phase space reconstruction.\n")

  # Step 4: Reconstruct phase space
  takens <- buildTakens(data, embedding.dim = M, time.lag = tau)
  cat("Dimensions of reconstructed phase space for ", var_name, ":", dim(takens), "\n")

  # Step 5: Visualize the phase space
  if (ncol(takens) >= 3) {
    scatterplot3d(takens[, 1], takens[, 2], takens[, 3], 
                  color.symbols = "blue", 
                  xlab = paste(var_name, "(t)"), 
                  ylab = paste(var_name, "(t+tau)"), 
                  zlab = paste(var_name, "(t+2tau)"), 
                  main = paste(var_name, "Phase Space"))
    # Interactive 3D plot
    plot3d(takens[, 1], takens[, 2], takens[, 3], 
           col = "blue", size = 0.5, main = paste("Interactive", var_name, "Phase Space"))
  } else {
    plot(takens[, 1], takens[, 2], type = "l", col = "blue", 
         xlab = paste(var_name, "(t)"), ylab = paste(var_name, "(t+tau)"), 
         main = paste(var_name, "Phase Space (2D)"))
  }

  # Step 6: Calculate correlation dimension
  corr_dim_obj <- corrDim(data, min.embedding.dim = M, max.embedding.dim = M, 
                          time.lag = tau, min.radius = sd_data / 50, 
                          max.radius = sd_data / 2, n.points = 10)
  corr_dim <- estimate(corr_dim_obj)

  # Step 7: Surrogate data analysis for robustness
  set.seed(123)
  surrogate_data <- sample(data, length(data), replace = FALSE)
  corr_dim_surrogate_obj <- corrDim(surrogate_data, min.embedding.dim = M, max.embedding.dim = M, 
                                    time.lag = tau, min.radius = sd_data / 50, 
                                    max.radius = sd_data / 2, n.points = 10)
  corr_dim_surrogate <- estimate(corr_dim_surrogate_obj)

  cat("Correlation Dimension for ", var_name, ":", corr_dim, "\n")
  cat("Correlation Dimension for surrogate data:", corr_dim_surrogate, "\n")
  cat("If the original correlation dimension is significantly lower than the surrogate, the result is more robust (Module 7).\n")

  return(list(tau = tau, M = M, takens = takens, corr_dim = corr_dim, corr_dim_surrogate = corr_dim_surrogate))
}

# Perform phase space reconstruction for humidity with diagnostic steps
humidity_result <- perform_phase_space_reconstruction_humidity(humidity, "Humidity")
```




3. Reconstruction for temporary, humidity and hive power
```{r}
# Helper function to find the first local minimum of ACF
find_acf_local_min <- function(ts, lag.max) {
  acf_vals <- acf(ts, lag.max = lag.max, plot = FALSE)$acf[-1]
  for (i in 2:(length(acf_vals) - 1)) {
    if (acf_vals[i] < acf_vals[i - 1] && acf_vals[i] < acf_vals[i + 1]) {
      return(i)
    }
  }
  below_threshold <- which(acf_vals < 0.2)
  if (length(below_threshold) > 0) {
    return(min(below_threshold))
  }
  return(lag.max / 2)
}

# Function to perform phase space reconstruction for a single variable
perform_phase_space_reconstruction <- function(data, var_name) {
  # Check data for potential issues
  cat("Summary of ", var_name, " data:\n")
  print(summary(data))
  cat("Standard deviation of ", var_name, ":", sd(data), "\n")
  if (any(is.na(data))) stop("Data contains NA values, please clean the data.")
  if (sd(data) == 0) stop("Data has zero variance, cannot perform phase space reconstruction.")

  # Calculate standard deviation for parameter setting
  sd_data <- sd(data)
  if (is.na(sd_data) || sd_data == 0) sd_data <- (max(data) - min(data)) / 4

  # Step 1: Determine time delay (tau) using ACF and AMI
  tau_acf <- find_acf_local_min(data, lag.max = 100)
  plot(acf(data, lag.max = 100, plot = FALSE), type = "h", main = paste("ACF Plot for", var_name))
  abline(h = 0.2, col = "red", lty = 2)

  tau_ami <- timeLag(data, technique = "ami", lag.max = 100, do.plot = TRUE)
  if (inherits(tau_ami, "try-error")) tau_ami <- tau_acf + 2

  cat("For ", var_name, ":\n")
  cat("ACF-based tau:", tau_acf, "\nAMI-based tau:", tau_ami, "\n")
  cat("We choose AMI-based tau (", tau_ami, ") as it is more suitable for nonlinear systems (Wiltshire, 2025).\n")
  tau <- tau_ami

  # Step 2: Determine embedding dimension (M) using estimateEmbeddingDim
  emb_dim <- estimateEmbeddingDim(data, time.lag = tau, max.embedding.dim = 10, do.plot = TRUE)
  if (is.na(emb_dim)) {
    cat("Warning: estimateEmbeddingDim returned NA for ", var_name, ". Setting default M = 3.\n")
    emb_dim <- 3
  }
  M <- max(emb_dim, 3)
  cat("Estimated M for ", var_name, ":", emb_dim, "\n")
  cat("We choose M =", M, "as it is determined by Cao's method via estimateEmbeddingDim (Cao, 1997).\n")

  # Step 3: Reconstruct phase space
  takens <- buildTakens(data, embedding.dim = M, time.lag = tau)
  cat("Dimensions of reconstructed phase space for ", var_name, ":", dim(takens), "\n")

  # Step 4: Visualize the phase space
  if (ncol(takens) >= 3) {
    scatterplot3d(takens[, 1], takens[, 2], takens[, 3], 
                  color.symbols = "blue", 
                  xlab = paste(var_name, "(t)"), 
                  ylab = paste(var_name, "(t+tau)"), 
                  zlab = paste(var_name, "(t+2tau)"), 
                  main = paste(var_name, "Phase Space"))
    # Interactive 3D plot
    plot3d(takens[, 1], takens[, 2], takens[, 3], 
           col = "blue", size = 0.5, main = paste("Interactive", var_name, "Phase Space"))
  } else {
    plot(takens[, 1], takens[, 2], type = "l", col = "blue", 
         xlab = paste(var_name, "(t)"), ylab = paste(var_name, "(t+tau)"), 
         main = paste(var_name, "Phase Space (2D)"))
  }

  # Step 5: Calculate correlation dimension
  corr_dim_obj <- corrDim(data, min.embedding.dim = M, max.embedding.dim = M, 
                          time.lag = tau, min.radius = sd_data / 50, 
                          max.radius = sd_data / 2, n.points = 10)
  corr_dim <- estimate(corr_dim_obj)

  # Step 6: Surrogate data analysis for robustness
  set.seed(123)
  surrogate_data <- sample(data, length(data), replace = FALSE)
  corr_dim_surrogate_obj <- corrDim(surrogate_data, min.embedding.dim = M, max.embedding.dim = M, 
                                    time.lag = tau, min.radius = sd_data / 50, 
                                    max.radius = sd_data / 2, n.points = 10)
  corr_dim_surrogate <- estimate(corr_dim_surrogate_obj)

  cat("Correlation Dimension for ", var_name, ":", corr_dim, "\n")
  cat("Correlation Dimension for surrogate data:", corr_dim_surrogate, "\n")
  cat("If the original correlation dimension is significantly lower than the surrogate, the result is more robust (Module 7).\n")

  return(list(tau = tau, M = M, takens = takens, corr_dim = corr_dim, corr_dim_surrogate = corr_dim_surrogate))
}

# Perform phase space reconstruction for temperature, humidity, and hive_power
temp_result <- perform_phase_space_reconstruction(temperature, "Temperature")
humidity_result <- perform_phase_space_reconstruction(humidity, "Humidity")
hive_power_result <- perform_phase_space_reconstruction(hive_power, "Hive Power")
```
4. Sensitivity Analysis for Temperature, Humidity, and Hive Power
```{r}
# Step 4: Sensitivity Analysis for Temperature, Humidity, and Hive Power

# Define ranges for tau and M
tau_range <- seq(2, 8, by = 2)  # Test tau values: 2, 4, 6, 8
M_range <- seq(2, 6, by = 2)    # Test M values: 2, 4, 6

# Function to perform sensitivity analysis for a single variable
perform_sensitivity_analysis <- function(data, var_name, tau_range, M_range) {
  # Initialize matrices to store correlation dimensions
  results <- matrix(NA, nrow = length(tau_range), ncol = length(M_range))
  results_surrogate <- matrix(NA, nrow = length(tau_range), ncol = length(M_range))
  
  # Calculate standard deviation for parameter setting
  sd_data <- sd(data)
  if (is.na(sd_data) || sd_data == 0) sd_data <- (max(data) - min(data)) / 4

  # Loop over tau and M values
  for (i in 1:length(tau_range)) {
    for (j in 1:length(M_range)) {
      # Reconstruct phase space with current tau and M (original data)
      takens <- buildTakens(data, embedding.dim = M_range[j], time.lag = tau_range[i])
      
      # Calculate correlation dimension (original data)
      corr_dim_obj <- corrDim(data, min.embedding.dim = M_range[j], max.embedding.dim = M_range[j], 
                              time.lag = tau_range[i], min.radius = sd_data / 50, 
                              max.radius = sd_data / 2, n.points = 10)
      corr_dim <- estimate(corr_dim_obj)
      results[i, j] <- ifelse(inherits(corr_dim, "try-error"), NA, corr_dim)

      # Calculate correlation dimension for surrogate data
      set.seed(123)
      surrogate_data <- sample(data, length(data), replace = FALSE)
      takens_surrogate <- buildTakens(surrogate_data, embedding.dim = M_range[j], time.lag = tau_range[i])
      corr_dim_surrogate_obj <- corrDim(surrogate_data, min.embedding.dim = M_range[j], max.embedding.dim = M_range[j], 
                                        time.lag = tau_range[i], min.radius = sd_data / 50, 
                                        max.radius = sd_data / 2, n.points = 10)
      corr_dim_surrogate <- estimate(corr_dim_surrogate_obj)
      results_surrogate[i, j] <- ifelse(inherits(corr_dim_surrogate, "try-error"), NA, corr_dim_surrogate)
    }
  }

  # Print the results matrices for analysis
  cat("Correlation Dimension Sensitivity for ", var_name, " (Original Data):\n")
  cat("Rows: tau =", tau_range, "\n")
  cat("Columns: M =", M_range, "\n")
  print(results)
  cat("\n")

  cat("Correlation Dimension Sensitivity for ", var_name, " (Surrogate Data):\n")
  cat("Rows: tau =", tau_range, "\n")
  cat("Columns: M =", M_range, "\n")
  print(results_surrogate)
  cat("\n")

  # Plot sensitivity analysis as heatmaps with a color palette
  # Original data
  heatmap(results, Rowv = NA, Colv = NA, xlab = "Embedding Dimension (M)", 
          ylab = "Time Delay (tau)", main = paste(var_name, "Corr. Dim. Sensitivity (Original)"), 
          col = colorRampPalette(c("lightblue", "blue", "darkblue"))(100))
  
  # Surrogate data
  heatmap(results_surrogate, Rowv = NA, Colv = NA, xlab = "Embedding Dimension (M)", 
          ylab = "Time Delay (tau)", main = paste(var_name, "Corr. Dim. Sensitivity (Surrogate)"), 
          col = colorRampPalette(c("lightblue", "blue", "darkblue"))(100))

  return(list(original = results, surrogate = results_surrogate))
}

# Perform sensitivity analysis for each variable
temp_sensitivity <- perform_sensitivity_analysis(temperature, "Temperature", tau_range, M_range)
humidity_sensitivity <- perform_sensitivity_analysis(humidity, "Humidity", tau_range, M_range)
hive_power_sensitivity <- perform_sensitivity_analysis(hive_power, "Hive Power", tau_range, M_range)
```

phase space reconstruction with specific 
```{r}
# Function to perform phase space reconstruction with specified tau and M
perform_phase_space_reconstruction <- function(data, var_name, tau, M) {
  # Step 1: Check data characteristics
  cat("Summary of ", var_name, " data:\n")
  print(summary(data))
  cat("Standard deviation of ", var_name, ":", sd(data), "\n")
  cat("Variance of ", var_name, ":", var(data), "\n")
  if (any(is.na(data))) stop("Data contains NA values, please clean the data.")
  if (sd(data) == 0) stop("Data has zero variance, cannot perform phase space reconstruction.")

  # Plot the time series to inspect its behavior
  plot(data, type = "l", col = "green", xlab = "Time", ylab = paste(var_name), 
       main = paste("Time Series of", var_name))

  # Plot histogram to inspect distribution
  hist(data, breaks = 30, col = "lightgreen", xlab = paste(var_name), 
       main = paste("Histogram of", var_name))

  # Calculate standard deviation for parameter setting
  sd_data <- sd(data)
  if (is.na(sd_data) || sd_data == 0) sd_data <- (max(data) - min(data)) / 4

  # Step 2: Use specified tau and M
  cat("Using specified tau =", tau, "and M =", M, "for", var_name, "\n")

  # Step 3: Reconstruct phase space
  takens <- buildTakens(data, embedding.dim = M, time.lag = tau)
  cat("Dimensions of reconstructed phase space for ", var_name, ":", dim(takens), "\n")

  # Step 4: Visualize the phase space
  if (ncol(takens) >= 3) {
    scatterplot3d(takens[, 1], takens[, 2], takens[, 3], 
                  color = "blue", 
                  xlab = paste(var_name, "(t)"), 
                  ylab = paste(var_name, "(t+tau)"), 
                  zlab = paste(var_name, "(t+2tau)"), 
                  main = paste(var_name, "Phase Space"))
    # Interactive 3D plot
    plot3d(takens[, 1], takens[, 2], takens[, 3], 
           col = "blue", size = 0.5, main = paste("Interactive", var_name, "Phase Space"))
  } else {
    plot(takens[, 1], takens[, 2], type = "l", col = "blue", 
         xlab = paste(var_name, "(t)"), ylab = paste(var_name, "(t+tau)"), 
         main = paste(var_name, "Phase Space (2D)"))
  }

  # Step 5: Calculate correlation dimension
  corr_dim_obj <- corrDim(data, min.embedding.dim = M, max.embedding.dim = M, 
                          time.lag = tau, min.radius = sd_data / 50, 
                          max.radius = sd_data / 2, n.points = 10)
  corr_dim <- estimate(corr_dim_obj)

  # Step 6: Surrogate data analysis for robustness
  set.seed(123)
  surrogate_data <- sample(data, length(data), replace = FALSE)
  corr_dim_surrogate_obj <- corrDim(surrogate_data, min.embedding.dim = M, max.embedding.dim = M, 
                                    time.lag = tau, min.radius = sd_data / 50, 
                                    max.radius = sd_data / 2, n.points = 10)
  corr_dim_surrogate <- estimate(corr_dim_surrogate_obj)

  # Step 7: Print results
  cat("Results for ", var_name, ":\n")
  cat("Tau =", tau, "\n")
  cat("M =", M, "\n")
  cat("Correlation Dimension =", corr_dim, "\n")
  cat("Correlation Dimension (Surrogate) =", corr_dim_surrogate, "\n")
  cat("If the original correlation dimension is significantly lower than the surrogate, the result is more robust (Module 7).\n")
  cat("\n")

  return(list(tau = tau, M = M, takens = takens, corr_dim = corr_dim, corr_dim_surrogate = corr_dim_surrogate))
}

# Perform phase space reconstruction with recommended parameters
temp_result <- perform_phase_space_reconstruction(temperature, "Temperature", tau = 2, M = 6)
humidity_result <- perform_phase_space_reconstruction(humidity, "Humidity", tau = 2, M = 2)
hive_power_result <- perform_phase_space_reconstruction(hive_power, "Hive Power", tau = 2, M = 2)
```
3D-plot for hive_power
```{r}
# Required packages (ensure these are loaded)
library(nonlinearTseries)
library(scatterplot3d)
library(rgl)

# Step 1: Recompute tau for hive_power using ACF to find periodicity
acf_hive_power <- acf(hive_power, lag.max = 1440, plot = FALSE)  # Assuming 1440 points per day (24 hours)
acf_peaks <- which(diff(sign(diff(acf_hive_power$acf))) == -2) + 1  # Find peaks in ACF
if (length(acf_peaks) > 0) {
  tau_periodic <- acf_peaks[1]  # Take the first peak as the period
} else {
  tau_periodic <- 360  # Default to 360 if no clear period
}
cat("Estimated period (tau) from ACF for Hive Power:", tau_periodic, "\n")

# Step 2: Reconstruct phase space for hive_power with tau = 360, M = 3
tau <- 360  # 6-hour intervals, assuming 1440 points per day
M <- 3      # 3D plot to better visualize periodicity
takens <- buildTakens(hive_power, embedding.dim = M, time.lag = tau)
cat("Dimensions of reconstructed phase space for Hive Power:", dim(takens), "\n")

# Step 3: Visualize the phase space
# 3D plot with lines
scatterplot3d(takens[, 1], takens[, 2], takens[, 3], 
              color = "blue", type = "l",  # Use lines to show trajectory
              xlab = "Hive Power(t)", 
              ylab = "Hive Power(t+tau)", 
              zlab = "Hive Power(t+2tau)", 
              main = "Hive Power Phase Space (tau = 360, M = 3)")

# Interactive 3D plot
plot3d(takens[, 1], takens[, 2], takens[, 3], 
       col = "blue", size = 0.5, main = "Interactive Hive Power Phase Space (tau = 360, M = 3)")

# Interactive 3D plot with a subset of points to reduce overlap
plot3d(takens[1:200, 1], takens[1:200, 2], takens[1:200, 3], 
       col = "blue", size = 0.5, main = "Interactive Hive Power Phase Space (First 200 Points, tau = 360, M = 3)")
```


```{r}
# Step 5: Save Results for Temperature, Humidity, and Hive Power

# Create a data frame with results
results_table <- data.frame(
  Metric = c("Tau (Temperature)", "Tau (Humidity)", "Tau (Hive Power)",
             "M (Temperature)", "M (Humidity)", "M (Hive Power)",
             "Corr. Dim. (Temperature)", "Corr. Dim. (Humidity)", "Corr. Dim. (Hive Power)",
             "Corr. Dim. (Temp Surrogate)", "Corr. Dim. (Humidity Surrogate)", "Corr. Dim. (Hive Power Surrogate)"),
  Value = c(temp_result$tau, humidity_result$tau, hive_power_result$tau,
            temp_result$M, humidity_result$M, hive_power_result$M,
            temp_result$corr_dim, humidity_result$corr_dim, hive_power_result$corr_dim,
            temp_result$corr_dim_surrogate, humidity_result$corr_dim_surrogate, hive_power_result$corr_dim_surrogate)
)

# Add a note about humidity data
cat("Note: These results use recommended parameters from sensitivity analysis.\n")
cat("Humidity's previous high correlation dimension (7.530213) suggested noise; using tau = 2, M = 2 may provide a more accurate estimate.\n")

# Save to CSV
write.csv(results_table, "single_variable_phase_space_results_updated.csv", row.names = FALSE)

# Print the results table for reference
cat("Results Table:\n")
print(results_table)
```


```{r}

```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

